A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-01-08 doc/large_strain.tex
Rev2 minor point 6

In this contribution, we proposed and numerically investigated several matrix-free implementations of tangent operators for finite-strain elasticity with heterogeneous materials.
The implementation that caches the material part of the fourth-order spatial tangent stiffness tensor together with the second-order Kirchhoff stress was shown to be faster than the matrix-based approach for quadratic elements in 3D and cubic in 3D.
This gives hope that the matrix-free implementation of the tangent operator can be applied to any constitutive model which operates with the material part of the fourth-order spatial tangent stiffness tensor on the quadrature point level.

>>>>

In this contribution, we proposed and numerically investigated several matrix-free implementations of tangent operators for finite-strain elasticity with heterogeneous materials.
The implementation that caches the material part of the fourth-order spatial tangent stiffness tensor together with the second-order Kirchhoff stress was shown to be faster than the matrix-based approach for quadratic elements in 3D and cubic {\color{red}elements} in 3D.
This gives hope that the matrix-free implementation of the tangent operator can be applied to any constitutive model which operates with the material part of the fourth-order spatial tangent stiffness tensor on the quadrature point level.
